Quality Definitions of Qualities

### 2019-10-23 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Added van Vliet reference to new correctness def, to clarify the source
Some reformatting to fix overlong lines

\begin{defn} \label{CorrectDefnSelected}
  A software is correct if it functions according to its specified functional
  and non-functional specification \cite{GhezziEtAl2003}.
\end{defn}

@@

\begin{defn}
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}.
\end{defn}

@@

\subsubsection{Discussion}
There is no direct tool or
method for measuring correctness. One way of building confidence in correctness
is by reviewing to ensure that each requirement stated is one that the
stakeholders and experts desire.  By maintaining traceability, consistency and
unambiguity, we can reduce the occurrence of errors and make the goal of
reviewing for correctness easier.\\
 The quality of a software's operation is dependent on the degree of correctness \cite{berander2005software}. Correctness and reliability are said to have dependencies, such that if a system exhibits a high degree of correctness then it tends to be reliable (\cite{GhezziEtAl2003}).

\subsection{Verifiability}
\begin{itemize}
	\item{Definition 1:} A software is verifiable if its properties can be verified (\cite{GhezziEtAl2003}).\\
	\item{Definition 2:} Attributes of software that relate to the effort needed for validating the modified software (\cite{berander2005software}).\\
	\item{Definition 3:}) The degree to which a system or component facilitates the establishment of test criteria and the performance of tests to determine whether those criteria have been met (\cite{IEEEStdGlossarySET1990}).\\
	\item{Definition 4:}  The degree to which a requirement is stated in terms that permit establishment of test criteria and performance (\cite{IEEEStdGlossarySET1990}).\\
	\item{Definition 5:} Ease of performing testing on a software product or system (\cite{IEEEStdGlossarySET1990}).\\
	\item{\textbf{Proposed definition}:} Combo of definitions 4 and 5 ?\\
\end{itemize}
\subsubsection{Discussion}
Verifiability involves ``solving the equations right''~\cite[p.~23]{Roache1998};
it benefits from rational documentation that systematically shows, with explicit
traceability, how the governing equations are transformed into code.
\oo{Verifiability is sometimes referred to as testability, so I culled some testability definitions here}\\
\subsection{Validatability}
\begin{itemize}
\item{Definition 1:} Validatability of a software is the degree of ease in validating(checking) that software meets user needs.\\
\item{Definition 2:} Validatability means ``solving the right equations''~\cite[p.~23]{Roache1998}.
\oo{question about this definition}\\
\item{Definition 3:} The degree of ease of evaluating software products or system to determine whether it satisfies specified business requirements. \url{http://softwaretestingfundamentals.com/verification-vs-validation/}\\
\oo{Here I tweaked the meaning of validation to suit validatability}\\
\oo{Only a few resource on validatability}\\
\item{\textbf{Proposed definition}:} Definition 3
\end{itemize}
\subsubsection{Discussion}
Validatability is improved by a rational process via clear documentation of the
theory and assumptions, along with an explicit statement of the systematic steps
required for experimental validation.

@@

\subsection{Robustness}
\begin{defn}
The degree to which a system or component can function correctly in the presence of invalid inputs or stressful environmental conditions \cite{IEEEStdGlossarySET1990}.\\
\end{defn}
\begin{defn}
The quality can be further informally refined as the ability of a software to keep an acceptable behavior, expressed in terms of robustness requirements, in spite of exceptional or unforeseen execution conditions (such as the unavailability of system resources, communication failures, invalid or stressful inputs, etc.) \cite{fernandez2005model}.\\
\end{defn}
\begin{defn}
Code possesses the characteristic of robustness to the extent that it can continue to perform despite some violation of the assumptions in its specification \cite{boehm2007software}.
\end{defn}
\begin{defn}
A program is robust if it behaves "reasonably", even in circumstances that were not anticipated in the requirements specification - for example, when it encounters incorrect input data or some hardware malfunction \cite{ghezzi1991fundamentals}\\
\end{defn}

>>>>

\begin{defn} \label{CorrectDefnSelected}
  A software is correct if it functions according to its specified functional
  and non-functional specification \citep{GhezziEtAl2003}.
\end{defn}

@@

\begin{defn}
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

@@

\subsubsection{Discussion}

There is no direct tool or method for measuring correctness. One way of building
confidence in correctness is by reviewing to ensure that each requirement stated
is one that the stakeholders and experts desire.  By maintaining traceability,
consistency and unambiguity, we can reduce the occurrence of errors and make the
goal of reviewing for correctness easier.

The quality of a software's operation is dependent on the degree of correctness
\cite{berander2005software}. Correctness and reliability are said to have
dependencies, such that if a system exhibits a high degree of correctness then
it tends to be reliable (\cite{GhezziEtAl2003}).

\subsection{Verifiability}
\begin{itemize}
\item{Definition 1:} A software is verifiable if its properties can be verified
  (\cite{GhezziEtAl2003}).
\item{Definition 2:} Attributes of software that relate to the effort needed for
  validating the modified software (\cite{berander2005software}).
\item{Definition 3:}) The degree to which a system or component facilitates the
  establishment of test criteria and the performance of tests to determine
  whether those criteria have been met (\cite{IEEEStdGlossarySET1990}).
\item{Definition 4:} The degree to which a requirement is stated in terms that
  permit establishment of test criteria and performance
  (\cite{IEEEStdGlossarySET1990}).
\item{Definition 5:} Ease of performing testing on a software product or system
  (\cite{IEEEStdGlossarySET1990}).
\item{\textbf{Proposed definition}:} Combo of definitions 4 and 5 ?
\end{itemize}
\subsubsection{Discussion}
Verifiability involves ``solving the equations right''~\cite[p.~23]{Roache1998};
it benefits from rational documentation that systematically shows, with explicit
traceability, how the governing equations are transformed into code.
\oo{Verifiability is sometimes referred to as testability, so I culled some
  testability definitions here}

\subsection{Validatability}

\begin{itemize}
\item{Definition 1:} Validatability of a software is the degree of ease in
  validating(checking) that software meets user needs.
\item{Definition 2:} Validatability means ``solving the right equations''~\cite[p.~23]{Roache1998}.
\oo{question about this definition}
\item{Definition 3:} The degree of ease of evaluating software products or
  system to determine whether it satisfies specified business
  requirements. \url{http://softwaretestingfundamentals.com/verification-vs-validation/}
  \oo{Here I tweaked the meaning of validation to suit validatability}
  \oo{Only a few resource on validatability}
\item{\textbf{Proposed definition}:} Definition 3
\end{itemize}

\subsubsection{Discussion}

Validatability is improved by a rational process via clear documentation of the
theory and assumptions, along with an explicit statement of the systematic steps
required for experimental validation.

@@

\subsection{Robustness}
\begin{defn}
  The degree to which a system or component can function correctly in the
  presence of invalid inputs or stressful environmental conditions
  \cite{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
  The quality can be further informally refined as the ability of a software to
  keep an acceptable behavior, expressed in terms of robustness requirements, in
  spite of exceptional or unforeseen execution conditions (such as the
  unavailability of system resources, communication failures, invalid or
  stressful inputs, etc.) \cite{fernandez2005model}.
\end{defn}
\begin{defn}
  Code possesses the characteristic of robustness to the extent that it can
  continue to perform despite some violation of the assumptions in its
  specification \cite{boehm2007software}.
\end{defn}
\begin{defn}
  A program is robust if it behaves "reasonably", even in circumstances that
  were not anticipated in the requirements specification - for example, when it
  encounters incorrect input data or some hardware malfunction
  \cite{ghezzi1991fundamentals}
\end{defn}
